---
title: "Milestone Report"
author: "Rodrigo Franco Fuentes"
date: "27/10/2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
#Packages
#library(dplyr)
#library(tidyr)
#library(tidytext)
library(tidyverse)
#library(ggplot2)
library(igraph)
library(tidytext)
```
## Demonstrate that I have downloaded the data, Basic report of summary statistics using the data sets
There are three sources of data: Blog, News and Tweet. Each has an entry corresponding different formats, Blog being the longest, Tweet the shortest. In terms of number of words the three texts are similar. As part of the document analysis data has been partially tidied, removing stop words, although these may become handy later. 
Tidy data should be valuable for establishing tone and thematical clustering techniques we hope will help increase the accuracy of the text prediction app. 


```{r , echo = FALSE, cache = TRUE}
T1 <- read.table(file = "Table1.csv")
T1
```
## Report Findings
The following table shows the ocurrences of specific values for each 100,000 tidy words. From a glance tweet and blog seem to be more sentiment driven with a higher frequency of words such as love, happy, life. Retweet or "rt", is the third most common "word", which signals a need for further cleaning of the data assuming it would bring incorrect predictions outside of a tweeter prediction app context.  

```{r pressure, echo =  FALSE, cache = TRUE}
T2 <- read.csv(file = "Table2.csv")
T2[,-1]
```
## Common bigrams 
Further procesing will require n-grams, here we can see the most common bigrams in tidy Blog data. We may need to go back on the tidying since many of the words we want to predict may be stop words. 





## Going further, plans on prediction app

The main method of predicting text will be, in principle, a Katz back off model, attempting further refinements with latent Dirichlet allocation for cluster subsetting. A sentiment subseting may also be tried.

